---
title: "AI Agents Demo: Autonomous Data Cleaning & EDA"
subtitle: "R Wrapper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

## Setup

This notebook uses `reticulate` to call the Python agent from R.
Make sure the Python virtual environment is set up first (see README).

```{r}
library(reticulate)

# Point to the project's Python venv
use_virtualenv("../.venv", required = TRUE)

# Load the R wrapper functions
source("eda_agent.R")
```

## Part 1: Configure the LLM

Pick your provider. For AWS Bedrock (no API key needed if AWS CLI is configured):

```{r}
eda_setup(provider = "bedrock", region = "eu-north-1")
```

Other options:
```r
# eda_setup(provider = "openai")
# eda_setup(provider = "anthropic")
# eda_setup(provider = "groq")
```

## Part 2: Load a CSV

```{r}
csv_path <- "your_data.csv"  # <-- change this!

df <- eda_load_csv(csv_path)
cat(sprintf("Loaded: %d rows x %d columns\n", nrow(df), ncol(df)))
head(df)
```

## Part 3: Inspect the Data

```{r}
inspection <- eda_inspect(df)

# Show the profile (first 500 chars)
cat(substr(inspection$profile, 1, 500), "\n...")
```

```{r}
# Show detected issues
issues <- inspection$issues

cat("Missing values:\n")
for (col in names(issues$missing_pct)) {
  pct <- issues$missing_pct[[col]]
  if (pct > 0) cat(sprintf("  %s: %.1f%%\n", col, pct))
}

cat(sprintf("\nDuplicate rows: %d\n", issues$duplicate_count))

if (length(issues$zero_variance) > 0) {
  cat(sprintf("Zero variance: %s\n", paste(issues$zero_variance, collapse = ", ")))
}

if (length(issues$high_cardinality) > 0) {
  cat(sprintf("High cardinality: %s\n", paste(issues$high_cardinality, collapse = ", ")))
}
```

## Part 4: Clean the Data (Manual)

```{r}
result <- eda_clean(df)
cleaned <- result$df

cat("Cleaning log:\n")
for (msg in result$log) cat(sprintf("  - %s\n", msg))

cat(sprintf("\nCleaned shape: %d rows x %d columns\n", nrow(cleaned), ncol(cleaned)))
head(cleaned)
```

## Part 5: EDA

```{r}
eda <- eda_analyze(cleaned)

cat("=== Numeric Statistics ===\n")
cat(eda$numeric_stats, "\n")

cat("\n=== Categorical Statistics ===\n")
cat(eda$categorical_stats, "\n")

cat("\n=== Correlation ===\n")
cat(eda$correlation, "\n")
```

```{r, results='asis'}
if (length(eda$figure_paths) > 0) {
  cat("### Generated Figures\n\n")
  for (path in eda$figure_paths) {
    cat(sprintf("![%s](%s)\n\n", basename(path), path))
  }
}
```

## Part 6: Full Agent Pipeline

This runs the complete LLM-driven pipeline — the agent decides what to clean and how.

```{r}
result <- eda_run(csv_path)
```

```{r, results='asis'}
# Display the report
if (!is.null(result$report_path) && file.exists(result$report_path)) {
  report <- readLines(result$report_path, warn = FALSE)
  cat(paste(report, collapse = "\n"))
}
```

## Part 7: View Agent Reasoning

```{r, results='asis'}
reasoning_path <- file.path("output", "reasoning.md")
if (file.exists(reasoning_path)) {
  reasoning <- readLines(reasoning_path, warn = FALSE)
  cat(paste(reasoning, collapse = "\n"))
}
```
